Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-04 soc_squeezing/cumulant_expansions.tex
rearranged some text in a derivation for clarity

  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}}
  \sum_{\p{\v J,\v K;\v m,\v n,\v r}} f_{\v m\v n\v r} P_{\v J} Q_{\v K},

@@

where $\v J$ and $\v K$ are respectively ordered lists of indices for
spins addressed by one and two single-spin operators in each term of
the expansion for $\S_{\v m} \S_{\v n}$ in \eqref{eq:SS_PP}; the sum
over $\p{\v r;\v m,\v n,s}$ denotes a sum over all values of $\v r$ with the restrictions

@@

the sum over $\p{\v J,\v K;\v m,\v n,\v r}$ denotes a sum over all
values of $\v J,\v K$ with the restrictions

@@

operators in $P_{\v j}$ and $P_{\v k}$ as prescribed by $\v r$, or

@@

where $\p{n}_k\equiv\prod_{j=0}^{k-1}\p{n-j}$ is a falling factorial;
and finally, similarly to the definition of $P_{\v j}$ in
\eqref{eq:SS_PP} we have

@@

where implicitly $\sum_a\rho^{\mu\nu}_a=r_{\mu\nu}$, as
$\p{\mu,\nu,a}$ essentially index a factor in \eqref{eq:Q_K_eta}, and

@@

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} \sum_{\p{\v\rho;\v r}}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} \S_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \ell_\mu
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \sum_\kappa\ell_\kappa }_{\sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.  For clarity, we note here that all indices
on
$m_\mu, n_\mu, r_{\mu\nu}, \rho^{\mu\nu}_\kappa, \eta_{\mu\nu\kappa},
\ell_\mu$ take on the same values as the indices on elements
$\sigma_\mu$ of some complete basis for single-spin operators; of
these, only the last index ($\kappa$) on
$\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ ever matches the index for
the identity element $\sigma_0\equiv\1$.

>>>>

  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} f_{\v m\v n\v r}
  \sum_{\p{\v J,\v K;\v m,\v n,\v r}} P_{\v J} Q_{\v K},

@@

where the sum over $\p{\v r;\v m,\v n,s}$ denotes a sum over all
values of $\v r$ with the restrictions

@@

@@

operators in $P_{\v j}$ and $P_{\v k}$ according to $\v r$, or

@@

with $\p{n}_k\equiv\prod_{j=0}^{k-1}\p{n-j}$ denoting a falling
factorial; $\v J$ and $\v K$ are respectively ordered lists of indices
for spins addressed by one and two single-spin operators in a term of
the product $P_{\v j} P_{\v k}$ with fixed $\v r$; the sum over
$\p{\v J,\v K;\v m,\v n,\v r}$ denotes a sum over all values of
$\v J,\v K$ with the restrictions
and finally, similarly to $P_{\v j}$ in \eqref{eq:SS_PP} we define

@@

where implicitly $\abs{\set{\rho^{\mu\nu}_a}}=r_{\mu\nu}$, as
$\p{\mu,\nu,a}$ essentially index a factor in \eqref{eq:Q_K_eta} and

@@

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} f_{\v m\v n\v r}
  \sum_{\p{\v\rho;\v r}} g_{\v\rho} \v\eta_{\v\rho}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  c_{\v\ell\v\rho} \S_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \ell_\mu
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \sum_\kappa\ell_\kappa }_{\sum_{\mu,\nu}\rho^{\mu\nu}_0}
\end{align}
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.  For clarity, we note here that all indices
on
$m_\mu, n_\mu, r_{\mu\nu}, \rho^{\mu\nu}_\kappa, \eta_{\mu\nu\kappa},
\ell_\mu$ take on the same values as the indices on elements
$\sigma_\mu$ of some complete basis for single-spin operators; of
these, only the last index ($\kappa$) on
$\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ ever matches the index for
the identity element $\sigma_0\equiv\1$.
